\chapter{Related Work}\label{chap:related_work}

\section{Introduction}

In this section, we will present general approaches to tag prediction, with a special focus on resource-based methods for broad folksonomies, that being our problem scope.

After reviewing the literature, we chose to divide these methods in categories for easier analysis:

\begin{itemize}

    \item \textbf{Association Rule Mining}: Methods that leverage the learning of data-based co-occurrence rules in the datasets.
    
    \item \textbf{Content-based Tag Propagation}: Methods that learn a representation of each resource based on their contents and use neighbour-based techniques to find similar points.
    
    \item \textbf{Resource-based tag propagation}: Similar to the above, but using other information to build representations for each resource.
    
    \item \textbf{Multi-label Classification/Ranking}: Methods based upon training multi-label classification algorithms, ranked or otherwise.
    
    \item \textbf{Topic Modelling/Tensor Factorization}: Methods based on finding a matrix and/or tensor based representation for resources and tags, and then applying factorization methods on those.
    
    \item \textbf{Graph-based}: Methods which model folksonomies as graphs and leverage graph-theoretic algorithms to predict tags for resources.
    
    \item \textbf{Other}: Other methods not in the previous categories.

\end{itemize}

As related to how authors name their particular approaches, one should be careful inasmuch as there is no apparent consensus as to what constitutes a \textit{recommendation} approach vis-a-vis a \textit{prediction} approach with respect to STSs. 

It is frequently the case in the literature that the word "recommendation" is used to refer to methods that use no user-specific information whatsoever and, conversely, words like "prediction" and "suggestion" used in cases where personalized recommendations are made.

\input{chapters/03_related_work/03_1_resource_centered_methods}

\input{chapters/03_related_work/03_3_other_aspects}

